Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-06-13 paper/paper.tex

Clusterization is complementary to prioritization; it helps to group
similar warnings reported by our infrastructure. We only clustered
``\lo'' warnings as ``\hi'' warnings produce messages that arise from
the test case, which are typically distinct.

Figure~\ref{fig:lo-truepositive} shows a test was originally
available in the \jsc code base.  The \radamsa fuzzing technique
mutated the test. In particular, it introduced the negative
long \texttt{-1770523502845470856} as a parameter of the
\texttt{view.getInt8()} method. Before the mutation, the
\texttt{view.getInt8()} method received a zero integer.
At the bottom of this figure, there is a sequence of
three elements that we use to characterize a warning: 1) the
identifier of an engine, 2) the exception it raises, and 3) the
message it produces on a ``\lo'' warning.  This sequence of triples
defines a warning signature that we use for clustering. It is worth
mentioning that we filter references to code in messages as to
increase ability to aggregate warnings. Any warnings, including this
one, that has this same signature will be included in the same
``bucket''. Considering the example from
Figure~\ref{fig:lo-truepositive}, the signature for that cluster will
be [(JavaScriptCore, ``RangeError'', ``byteOffset cannot be
  negative''), (SpiderMonkey, ``RangeError'', ``invalid or
  out-of-range index''), (V8, ``RangeError'', ``Offset is outside the
  bounds of the DataView'')].

>>>>

Clusterization is complementary to prioritization. It helps to group
similar warnings reported by our infrastructure. We only clustered
``\lo'' warnings as ``\hi'' warnings produce messages that arise from
the test case, which are typically distinct.
Figure~\ref{fig:lo-truepositive} shows a test that was originally
available in the \jsc suite. The \radamsa fuzzer mutated the test. It
introduced the negative long \CodeIn{-1770523502845470856} as a
parameter of the \CodeIn{view.getInt8()} method. Before the mutation,
the \CodeIn{view.getInt8()} method received zero as parameter.  At the
bottom of this figure, there is a sequence of three elements that we
use to characterize a warning: 1) the identifier of an engine, 2) the
exception it raises, and 3) the message it produces on a ``\lo''
warning.  This sequence of triples defines a warning signature that we
use for clustering. It is worth mentioning that we filter references
to code in messages as to increase ability to aggregate warnings. Any
warnings, including this one, that has this same signature will be
included in the same ``bucket''. Considering this particular example,
the signature for that cluster will be [(JavaScriptCore,
  ``RangeError'', ``byteOffset cannot be negative''), (SpiderMonkey,
  ``RangeError'', ``invalid or out-of-range index''), (V8,
  ``RangeError'', ``Offset is outside the bounds of the DataView'')].
